---
  title: "Weiss T, Taschner-Mandl S, Bileck A, Slany A et al. 
          Proteomics and transcriptomics of peripheral nerve tissue and cells
          unravel new aspects of the human Schwann cell repair phenotype. 
          Glia 2016 Dec;64(12):2133-2153. PMID: 27545331.
          Dataset re-analysis"
---
  
  ```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r libraries }

#if (!require("BiocManager", quietly = TRUE))
#  install.packages("BiocManager")

# The following initializes usage of Bioc devel
#BiocManager::install(version='devel')
#BiocManager::install("SurfR")
#BiocManager::install("TCGAbiolinks")
#devtools::install_github("auroramaurizio/SurfR")

#import the libraries
library(SurfR)
library(stringr)
library(openxlsx)
library(ggplot2)
```

## Download nerve injury GSE90711 metadata from GEO 

```{r GEO metadata }

mGSE90711 <- GEOmetadata(GSE = "GSE90711")
# Select rows by matching specific titles 
#SC vs fibroblast cell lines
#injured vs CTRL fascicles

unique(mGSE90711$GSM)

mGSE90711_cells <- mGSE90711[7:14, ]
mGSE90711_fascicle <- mGSE90711[1:6, ]

nrow(mGSE90711_fascicle)

# create new metadata column in order to remove unwanted special characters
# Add a new column 'CellType' based on the 'title' column
mGSE90711_cells$CellType <- ifelse(grepl("Schwann cells", mGSE90711_cells$title), "Schwann", 
                             ifelse(grepl("fibroblasts", mGSE90711_cells$title), "fibroblast", NA))

mGSE90711_fascicle$CellType <- ifelse(grepl("injured", mGSE90711_fascicle$title), "injured", 
                                   ifelse(grepl("CTRL", mGSE90711_fascicle$title), "CTRL", NA))


head(mGSE90711_fascicle)
# create new metadata column in order to remove unwanted special characters
unwanted_character <- " "
fx <- function(x) {
  str_split(string = x, pattern = unwanted_character)[[1]][1]
}

mGSE90711_cells$condition <- sapply(mGSE90711_cells$CellType, fx)
mGSE90711_cells <- as.data.frame(mGSE90711_cells)
mGSE90711_cells$condition <- as.factor(mGSE90711_cells$condition)


mGSE90711_fascicle$condition <- sapply(mGSE90711_fascicle$CellType, fx)
mGSE90711_fascicle <- as.data.frame(mGSE90711_fascicle)
mGSE90711_fascicle$condition <- as.factor(mGSE90711_fascicle$condition)

```

# Download count matrix from ArchS4

```{r GEO countmatrix cells }
cGSE90711_cells <- DownloadArchS4(mGSE90711_cells$GSM,
                             species = "human",
                             print_tsv = FALSE,
                             filename = NULL)

# Preview count matrix
head(cGSE90711_cells[, ])

```

```{r GEO countmatrix fascicle}
cGSE90711_fascicle <- DownloadArchS4(mGSE90711_fascicle$GSM,
                                  species = "human",
                                  print_tsv = FALSE,
                                  filename = NULL)

# Preview count matrix
head(cGSE90711_fascicle[, ])

```

## Explore the GEO dataset, look for batch effects with a PCA (Fig. 1B)

```{r GEO PCA cells }

# Plot pca
pdf("PCA_cGSE90711_GEO_cells.pdf")
SurfR::plotPCA(matrix = edgeR::cpm(cGSE90711_cells), metadata = mGSE90711_cells,
               dims = c(1, 2),
               color.by = "condition", shape.by = "condition",
               label = FALSE, main = "PCA cells GSE90711")
dev.off()


```


```{r GEO PCA fascicles }

# Plot pca
pdf("PCA_cGSE90711_GEO_fascicle.pdf")
SurfR::plotPCA(matrix = edgeR::cpm(cGSE90711_fascicle), metadata = mGSE90711_fascicle,
               dims = c(1, 2),
               color.by = "condition", shape.by = "condition",
               label = FALSE, main = "PCA fascicles GSE90711")
dev.off()


```

```{r GEO reorder }
# Extract the order of GSM identifiers from mGSE90711_cells
gsm_order_cells <- mGSE90711_cells$GSM

# Reorder the columns of cGSE90711 based on the gsm_order
cGSE90711_cells_ordered <- cGSE90711_cells[, gsm_order_cells]


# Extract the order of GSM identifiers from mGSE90711_fascicle
gsm_order_fascicle <- mGSE90711_fascicle$GSM

# Reorder the columns of cGSE90711 based on the gsm_order
cGSE90711_fascicle_ordered <- cGSE90711_fascicle[, gsm_order_fascicle]
```


# Perform DGE on the GEO cells dataset

```{r GEO cells DGE }
df_GEO_cells <- DGE(expression = cGSE90711_cells_ordered,
              metadata = mGSE90711_cells,
              Nreplica = 3,
              design = "~condition",
              condition = "condition",
              alpha = 0.05,
              TEST = "Schwann", CTRL ="fibroblast",
              output_tsv = FALSE)

# remove NA values
df_GEO_cells <- df_GEO_cells[!is.na(df_GEO_cells$padj), ]

# select only genes with a very Mean_CPM value < 0.5 in the control
#df_GEO_cells <- df_GEO_cells[df_GEO_cells$Mean_CPM_C < 0.5,]

# Detect SP amoung differentially expressed genes
fdr_GeneID_cells <- df_GEO_cells[df_GEO_cells$padj < 0.05, "GeneID"]
SP_GEO_cells <- Gene2SProtein(genes = fdr_GeneID_cells, input_type = "gene_name")
nrow(SP_GEO_cells)
#745 out of 5399 genes have a matching surface protein

nrow(df_GEO_cells)

fdrUP_GeneID_cells <- df_GEO_cells[df_GEO_cells$padj < 0.05 & df_GEO_cells$log2FoldChange > 0, "GeneID"]

SPup_GEO_cells <- Gene2SProtein(genes = fdrUP_GeneID_cells, input_type = "gene_name")
#443 out of 1832 genes have a matching surface protein # FC1
#495 out of 2845 genes have a matching surface protein # FC 0

nrow(ML_SPup_GEO_cells <- SPup_GEO_cells[grepl("machine learning", SPup_GEO_cells$Surfaceome.Label.Source),]) #334
nrow( SPup_GEO_cells[!grepl("machine learning", SPup_GEO_cells$Surfaceome.Label.Source),]) #161


fdrDW_GeneID_cells <- df_GEO_cells[df_GEO_cells$padj < 0.05 & df_GEO_cells$log2FoldChange < 0, "GeneID"]
SPdw_GEO_cells <- Gene2SProtein(genes = fdrDW_GeneID_cells, input_type = "gene_name")
#205 out of 1267 genes have a matching surface protein # FC -1
#250 out of 2554 genes have a matching surface protein # FC 0

write.xlsx(SPup_GEO_cells, "Supp_table_GSE90711_SPup_GEO_cells_FDR.xlsx")

```

```{r GEO fascicle DGE }
df_GEO_fascicle <- DGE(expression = cGSE90711_fascicle_ordered,
                       metadata = mGSE90711_fascicle,
                       Nreplica = 3,
                       design = "~condition",
                       condition = "condition",
                       alpha = 0.05,
                       TEST = "injured", CTRL ="CTRL",
                       output_tsv = FALSE)

# remove NA values
df_GEO_fascicle <- df_GEO_fascicle[!is.na(df_GEO_fascicle$padj), ]

# select only genes with a very Mean_CPM value < 0.5 in the control
#df_GEO_fascicle <- df_GEO_fascicle[df_GEO_fascicle$Mean_CPM_C < 0.5,]

# Detect SP amoung differentially expressed genes
fdr_GeneID_fascicle <- df_GEO_fascicle[df_GEO_fascicle$padj < 0.05, "GeneID"]
length(fdr_GeneID_fascicle)

SP_GEO_fascicle <- Gene2SProtein(genes = fdr_GeneID_fascicle, input_type = "gene_name")
#566 out of 4293 genes have a matching surface protein

fdrUP_GeneID_fascicle <- df_GEO_fascicle[df_GEO_fascicle$padj < 0.05 & df_GEO_fascicle$log2FoldChange > 0, "GeneID"]
SPup_GEO_fascicle <- Gene2SProtein(genes = fdrUP_GeneID_fascicle, input_type = "gene_name")
#203 out of 1373 genes have a matching surface protein FC > 1
#251 out of 2113 genes have a matching surface protein FC > 0

nrow(SPup_GEO_fascicle[grepl("machine learning", SPup_GEO_fascicle$Surfaceome.Label.Source),]) #149
nrow(SPup_GEO_fascicle[!grepl("machine learning", SPup_GEO_fascicle$Surfaceome.Label.Source),]) #102

fdrDW_GeneID_fascicle <- df_GEO_fascicle[df_GEO_fascicle$padj < 0.05 & df_GEO_fascicle$log2FoldChange < 0, "GeneID"]
SPdw_GEO_fascicle <- Gene2SProtein(genes = fdrDW_GeneID_fascicle, input_type = "gene_name")
# 315 out of 2180 genes have a matching surface protein FC < 0


write.xlsx(SPup_GEO_fascicle, "Supp_table_GSE90711_SPup_GEO_fascicle_FDR0.xlsx")
```

```{r venn }
common_rownames <- rownames(SPup_GEO_fascicle)[rownames(SPup_GEO_fascicle) %in% rownames(SPup_GEO_cells)]
SPup_GEO_common <- SPup_GEO_fascicle[common_rownames, ]
SPup_GEO_common$GeneID


S_list <- list(SPup_GEO_cells = rownames(SPup_GEO_cells),
               SPup_GEO_fascicle = rownames(SPup_GEO_fascicle))

pdf("Venn_GEO_cells_fascicles.pdf")
SVenn(S_list,
      cols.use = c("green", "blue"),
      opacity = 0.5,
      output_intersectionFile = FALSE)
dev.off()
```


## Perform the enrichment to carachterize UP and DOWN regulated genes

```{r permorm and graphycally represent the enrichment}

#library(enrichR)
#library(ggplot2)


dfList <- list(GEO_cells = as.data.frame(df_GEO_cells), 
               GEO_fascicle = as.data.frame(df_GEO_fascicle))

# perform the enrichment
Enrich <- Enrichment(dfList,
                     enrich.databases = c("GO_Biological_Process_2021"),
                     p_adj = 0.05, logFC = 1, save.results = TRUE)


# represent the enriched pathways as a barplot

pdf("Enrichment_barplot_GEO_cells_UP_allgenes.pdf", 7, 4)
Enrichment_barplot(Enrich$GEO_cells,
                   enrich.databases <- c("GO_Biological_Process_2021"),
                   p_adj = 0.05,
                   num_term = 10,
                   cond = "UP")
dev.off()

pdf("Enrichment_barplot_GEO_cells_DW_allgenes.pdf", 10, 4)
Enrichment_barplot(Enrich$GEO_cells,
                   enrich.databases <- c("GO_Biological_Process_2021"),
                   p_adj = 0.05,
                   num_term = 10,
                   cond = "DOWN")
dev.off()

pdf("Enrichment_barplot_GEO_fascicle_UP_allgenes.pdf", 7, 4)
Enrichment_barplot(Enrich$GEO_fascicle,
                   enrich.databases <- c("GO_Biological_Process_2021"),
                   p_adj = 0.05,
                   num_term = 10,
                   cond = "UP")
dev.off()

pdf("Enrichment_barplot_GEO_fascicle_DW_allgenes.pdf", 10, 4)
Enrichment_barplot(Enrich$GEO_fascicle,
                   enrich.databases <- c("GO_Biological_Process_2021"),
                   p_adj = 0.05,
                   num_term = 10,
                   cond = "DOWN")
dev.off()


```
## perform and graphically represent the enrichment of SPCG vs non SPCG 

```{r enrichment of SPCG vs non SPCG}


SP_GEO_cells_genes <- SP_GEO_cells$UniProt.gene
NSP_GEO_cells_genes <- df_GEO_cells$GeneID[!df_GEO_cells$GeneID %in% SP_GEO_cells_genes] 

df_SP_GEO_cells_genes <- df_GEO_cells[rownames(df_GEO_cells) %in% SP_GEO_cells_genes, ]
df_NSP_GEO_cells_genes <- df_GEO_cells[rownames(df_GEO_cells) %in% NSP_GEO_cells_genes, ]

dfListSP_GEO_cells <- list(SP_GEO_cells = as.data.frame(df_SP_GEO_cells_genes)) 

dfListNSP_GEO_cells <- list(NSP_GEO_cells = as.data.frame(df_NSP_GEO_cells_genes))

Enrich_GEO_BP <- Enrichment(dfListSP_GEO_cells,
                            enrich.databases = c("GO_Biological_Process_2021"),
                            p_adj = 0.05, logFC = 1, save.results = TRUE)


# biological process

SPvs_nSP_UP_GEO_BP <- Enrichment_barplot(Enrich_GEO_BP$SP_GEO_cells,
                                         enrich.databases <- c("GO_Biological_Process_2021"),
                                         p_adj = 0.05,
                                         num_term = 10)


pdf("Enrich_SPvs_nSP_UP_GEO_cells_BP_new.pdf",5.5,2)
print(SPvs_nSP_UP_GEO_BP +ggtitle("SP - GEO BP")+ 
        theme(
          legend.title = element_text(size = 6), # Adjust legend title font size
          legend.text = element_text(size = 6)   # Adjust legend text font size
        ) )
dev.off()


## nSP #########################################################################

Enrich_GEO_BP_nsp <- Enrichment(dfListNSP_GEO_cells,
                                enrich.databases = c("GO_Biological_Process_2021"),
                                p_adj = 0.05, logFC = 1, save.results = TRUE)


SPvs_nSP_DOWN_GEO_BP <- Enrichment_barplot(Enrich_GEO_BP_nsp$NSP_GEO_cells,
                                           enrich.databases <- c("GO_Biological_Process_2021"),
                                           p_adj = 0.05,
                                           num_term = 10)



pdf("Enrich_nSP_DOWN_GEO_cells_BP.pdf",5.5,2)
print(SPvs_nSP_DOWN_GEO_BP +ggtitle("nSP - GEO BP")+ 
        theme(
          legend.title = element_text(size = 6), # Adjust legend title font size
          legend.text = element_text(size = 6)   # Adjust legend text font size
        ) )
dev.off()

```


```{r GEO CC, MF }

Enrich_GEO_CC_nsp <- Enrichment(dfListNSP_GEO_cells,
                                enrich.databases = c("GO_Cellular_Component_2021"),
                                p_adj = 0.05, logFC = 1, save.results = TRUE)

Enrich_GEO_MF_nsp <- Enrichment(dfListNSP_GEO_cells,
                                enrich.databases = c("GO_Molecular_Function_2021"),
                                p_adj = 0.05, logFC = 1, save.results = TRUE)


SPvs_nSP_DOWN_GEO_CC <- Enrichment_barplot(Enrich_GEO_CC_nsp$NSP_GEO_cells,
                                           enrich.databases <- c("GO_Cellular_Component_2021"),
                                           p_adj = 0.05,
                                           num_term = 10)
print(SPvs_nSP_DOWN_GEO_CC +ggtitle("nSP - GEO CC")) 


SPvs_nSP_DOWN_GEO_MF <- Enrichment_barplot(Enrich_GEO_MF_nsp$NSP_GEO_cells,
                                           enrich.databases <- c("GO_Molecular_Function_2021"),
                                           p_adj = 0.05,
                                           num_term = 10)
print(SPvs_nSP_DOWN_GEO_MF +ggtitle("nSP - GEO MF")) 

```


## annotate our list of genes with cross-database identifiers


```{r GEO cells annotate SPID }
annotated_GEO <- Annotate_SPID(df_GEO_cells, "WikiPathway_2021_Human")
head(annotated_GEO, 10)

write.xlsx(annotated_GEO, "annotated_GEO_cells_WikiPathway_2021_Human.xlsx")
```

```{r GEO fascicle annotate SPID }
annotated_GEO <- Annotate_SPID(df_GEO_fascicle, "WikiPathway_2021_Human")
head(annotated_GEO, 10)

write.xlsx(annotated_GEO, "annotated_GEO_cells_WikiPathway_2021_Human.xlsx")
```


## Plot the fraction on SPCG coding for receptor, enzymes, transporters etc.

```{r Almen classification }
# Barplot of Almen classification


pdf("Almen_class_SPUP_GEO_cells.pdf")
Splot(SPup_GEO_cells,
      group.by = "Membranome.Almen.main-class",
      main = "Almen class Adj")
dev.off()


pdf("Almen_class_SPUP_GEO_fascicle.pdf")
Splot(SPup_GEO_fascicle,
      group.by = "Membranome.Almen.main-class",
      main = "Almen class Adj")
dev.off()

SPup <- SPup_GEO_cells[rownames(SPup_GEO_cells) %in% rownames(SPup_GEO_fascicle), ]
nrow(SPup)

pdf("Almen_class_SPUP_GEO_common.pdf")
Splot(SPup,
      group.by = "Membranome.Almen.main-class",
      main = "Almen class Adj")
dev.off()
```

```{r Almen classification }
####### enrichment of common SPCG ############
nrow(SPup)
all_SPup <- SPup$UniProt.gene
df_SP_GEO_cells_genes_all_comm <- df_GEO_cells[rownames(df_GEO_cells) %in% all_SPup, ]
ML_SPup <- SPup[grepl("machine learning", SPup$Surfaceome.Label.Source),]
ML_SPup <- ML_SPup$UniProt.gene
df_SP_GEO_cells_genes_ML <- df_GEO_cells[rownames(df_GEO_cells) %in% ML_SPup, ]
nrow(df_SP_GEO_cells_genes_ML)
nrow(df_SP_GEO_cells_genes_all_comm)

df_SP_GEO_cells_genes_ML_all <- list(SP_GEO_cells_ML = as.data.frame(df_SP_GEO_cells_genes_ML))



Enrich_GEO_BP_ML <- Enrichment(df_SP_GEO_cells_genes_ML_all,
                               enrich.databases = c("GO_Cellular_Component_2021"),
                               p_adj = 0.05, logFC = 1, save.results = TRUE)


Enrich_GEO_BP_ML$SP_GEO_cells_ML$fdr_up$GO_Cellular_Component_2021



Enrich_GEO_BP_ML_P <- Enrichment_barplot(Enrich_GEO_BP_ML$SP_GEO_cells_ML,
                                         enrich.databases = c("GO_Cellular_Component_2021"),
                                         p_adj = 0.05,
                                         num_term = 5, cond = "UP")


print(Enrich_GEO_BP_ML_P +ggtitle("SP - ML")+ 
        theme(
          legend.title = element_text(size = 6), 
          legend.text = element_text(size = 6)   
        ) )



pdf("ML_predicted_SP_common_CC_.pdf")
print(Enrich_GEO_CC_ML_P +ggtitle("common ML-pred SP CC")+ 
        theme(
          legend.title = element_text(size = 6), 
          legend.text = element_text(size = 6)   
        ) )
dev.off()


pdf("ML_predicted_SP_common_CC_.pdf", 7, 4)
Enrich_GEO_CC_ML_P
dev.off()

df_SP_GEO_cells_genes_all_comm$GeneID


df_SP_GEO_cells_genes_all <- list(SP_GEO_cells_all = as.data.frame(df_SP_GEO_cells_genes_all_comm))


Enrich_GEO_CC_all <- Enrichment(df_SP_GEO_cells_genes_all,
                                enrich.databases = c("GO_Cellular_Component_2021"),
                                p_adj = 0.05, logFC = 1, save.results = TRUE)


Enrich_GEO_CC_all_P <- Enrichment_barplot(Enrich_GEO_CC_all$SP_GEO_cells_all,
                                          enrich.databases = c("GO_Cellular_Component_2021"),
                                          p_adj = 0.05,
                                          num_term = 10, cond = "UP")


print(Enrich_GEO_CC_all_P +ggtitle("SP - common")+ 
        theme(
          legend.title = element_text(size = 6), 
          legend.text = element_text(size = 6)   
        ) )



pdf("SP_common_CC_.pdf", 5, 6)
print(Enrich_GEO_CC_all_P +ggtitle("common SP CC")+ 
        theme(
          legend.title = element_text(size = 6), 
          legend.text = element_text(size = 6)   
        ) )
dev.off()





Enrich_GEO_BP_all <- Enrichment(df_SP_GEO_cells_genes_all,
                                enrich.databases = c("GO_Biological_Process_2021"),
                                p_adj = 0.05, logFC = 1, save.results = TRUE)


Enrich_GEO_BP_all_P <- Enrichment_barplot(Enrich_GEO_BP_all$SP_GEO_cells_all,
                                          enrich.databases = c("GO_Biological_Process_2021"),
                                          p_adj = 0.05,
                                          num_term = 10, cond = "UP")



pdf("SP_common_CC_.pdf", 7,4)
Enrich_GEO_CC_all_P 
dev.off()

pdf("SP_common_BP_.pdf")
print(Enrich_GEO_BP_all_P +ggtitle("common SP BP")+ 
        theme(
          legend.title = element_text(size = 6), 
          legend.text = element_text(size = 6)   
        ) )
dev.off()

```


################################################################################
# Redo imposing a low SPCG expression in the control (Mean_CPM_C < 0.5)

################################################################################



# Perform DGE on the GEO dataset

```{r GEO cells }
df_GEO_cells <- DGE(expression = cGSE90711_cells_ordered,
                    metadata = mGSE90711_cells,
                    Nreplica = 3,
                    design = "~condition",
                    condition = "condition",
                    alpha = 0.05,
                    TEST = "Schwann", CTRL ="fibroblast",
                    output_tsv = FALSE)

# remove NA values
df_GEO_cells <- df_GEO_cells[!is.na(df_GEO_cells$padj), ]

# select only genes with a very Mean_CPM value < 0.5 in the control
df_GEO_cells <- df_GEO_cells[df_GEO_cells$Mean_CPM_C < 0.5,]

# Detect SP amoung differentially expressed genes
fdr_GeneID_cells <- df_GEO_cells[df_GEO_cells$padj < 0.05, "GeneID"]

SP_GEO_cells <- Gene2SProtein(genes = fdr_GeneID_cells, input_type = "gene_name")
#77 out of 350 genes have a matching surface protein

fdrUP_GeneID_cells <- df_GEO_cells[df_GEO_cells$padj < 0.05 & df_GEO_cells$log2FoldChange > 0, "GeneID"]
SPup_GEO_cells <- Gene2SProtein(genes = fdrUP_GeneID_cells, input_type = "gene_name")
#77 out of 350 genes have a matching surface protein

fdrDW_GeneID_cells <- df_GEO_cells[df_GEO_cells$padj < 0.05 & df_GEO_cells$log2FoldChange < 0, "GeneID"]
SPdw_GEO_cells <- Gene2SProtein(genes = fdrDW_GeneID_cells, input_type = "gene_name")
#The input genes do not have any match in the surfaceome database.


#write.xlsx(SPup_GEO_cells, "Supp_table_GSE90711_SPup_GEO_filt.xlsx")
```

```{r GEO fascicle }
df_GEO_fascicle <- DGE(expression = cGSE90711_fascicle_ordered,
                       metadata = mGSE90711_fascicle,
                       Nreplica = 3,
                       design = "~condition",
                       condition = "condition",
                       alpha = 0.05,
                       TEST = "injured", CTRL ="CTRL",
                       output_tsv = FALSE)

# remove NA values
df_GEO_fascicle <- df_GEO_fascicle[!is.na(df_GEO_fascicle$padj), ]

# select only genes with a very Mean_CPM value < 0.5 in the control
df_GEO_fascicle <- df_GEO_fascicle[df_GEO_fascicle$Mean_CPM_C < 0.5,]

# Detect SP amoung differentially expressed genes
fdr_GeneID_fascicle <- df_GEO_fascicle[df_GEO_fascicle$padj < 0.05, "GeneID"]

SP_GEO_fascicle <- Gene2SProtein(genes = fdr_GeneID_fascicle, input_type = "gene_name")
#20 out of 90 genes have a matching surface protein

fdrUP_GeneID_fascicle <- df_GEO_fascicle[df_GEO_fascicle$padj < 0.05 & df_GEO_fascicle$log2FoldChange > 0, "GeneID"]
SPup_GEO_fascicle <- Gene2SProtein(genes = fdrUP_GeneID_fascicle, input_type = "gene_name")
#20 out of 90 genes have a matching surface protein

fdrDW_GeneID_fascicle <- df_GEO_fascicle[df_GEO_fascicle$padj < 0.05 & df_GEO_fascicle$log2FoldChange < 0, "GeneID"]
SPdw_GEO_fascicle <- Gene2SProtein(genes = fdrDW_GeneID_fascicle, input_type = "gene_name")
#The input genes do not have any match in the surfaceome database.
```


```{r venn }
S_list <- list(SPup_GEO_cells = rownames(SPup_GEO_cells),
               SPup_GEO_fascicle = rownames(SPup_GEO_fascicle))

pdf("Venn_GEO_cells_fascicles_filtered.pdf")
SVenn(S_list,
      cols.use = c("green", "blue"),
      opacity = 0.5,
      output_intersectionFile = FALSE)
dev.off()

```

```{r common }
common_rownames <- rownames(SPup_GEO_fascicle)[rownames(SPup_GEO_fascicle) %in% rownames(SPup_GEO_cells)]
SPup_GEO_common <- SPup_GEO_fascicle[common_rownames, ]
SPup_GEO_common$GeneID
#"HLAG_HUMAN"  "5HT1E_HUMAN" "MCHR1_HUMAN"

# HLAG_HUMAN: https://www.sciencedirect.com/science/article/pii/S0969996122003448
# https://opencell.czbiohub.org/gene/ENSG00000204632

# 5HT1E_HUMAN: https://pubmed.ncbi.nlm.nih.gov/9125415/
# https://opencell.czbiohub.org/gene/ENSG00000168830

# MCHR1_HUMAN: https://www.sciencedirect.com/science/article/abs/pii/0196978195000088
# https://opencell.czbiohub.org/gene/ENSG00000128285

#pdf("Almen_class_SPUP_metacomb.pdf")
Splot(SPup_GEO_fascicle,
      group.by = "Membranome.Almen.main-class",
      main = "Almen class Adj")

Splot(SPup_GEO_cells,
      group.by = "Membranome.Almen.main-class",
      main = "Almen class Adj")

pdf("Almen_class_SPUP_GEO_common_filt.pdf")
Splot(SPup_GEO_common,
      group.by = "Membranome.Almen.main-class",
      main = "Almen class Adj")
dev.off()
```




